Open Peer Review

### 2019-09-25 manuscript.Rmd
update code, gitignore - RSOS df does not have all versions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

The database created from PeerJ uses reviews published from 21 February 2012 till
18 March 2019. These reviews come from 11 different scientific sections and contain a total
of 6800 articles. The reviews of PeerJ are structured differently from The Royal Society and
do not contain individual recommendations of the reviewers. Instead the recommendation of
the academic editor is displayed on the different versions of the manuscript. PeerJ does
publicize all the different versions of the submitted manuscripts opposed to The Royal
Society which only publishes the final accepted manuscript. The reviews of PeerJ do not
contain a set of standard questions, but use 4 different topic on which the reviewers are asked
to comment. These topics are; basic reporting, experimental design, validity of the findings
and comments for the author. The guidelines on which topic has to contain which information
seems not to be strictly defined and it is mainly up to the decision of the reviewer what
information to put in which section. Basic reporting and comments for the author sections
commonly contain the majority of the peer review. In some cases the reviewers refer to
attached documents that assumably were included in the correspondence, but these
documents are not publicized along the reviews. In these cases the data will be regarded
missing in the database.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(dplyr)
library(formattable)
library(tidyr)
library(ggplot2)
library(here)

here::here()

```

@@

```{r}
# Read open science and open biology rds datafiles
TRS_data_os <- readRDS(file = "royal_society_data_os.rds")
TRS_data_ob <- readRDS(file = "royal_society_data_ob.rds")

# Combine both datasets into one.
TRS_data <- rbind(TRS_data_os, TRS_data_ob)

PeerJ_data <- readRDS(file = "peerj_data.rds")

TRS_data_sorted <- TRS_data[ with( TRS_data , order ( df_link)),]

```

Older Royal Society journals have the comment: Note: This manuscript was transferred from another Royal Society journal without peer review.
What does this mean?
